An Incomplete Overview of Some Applications of Game Theory to Patient Flow

### 2014-05-14 paper.tex
Happy with introduction

The best known work applying Game Theory to Healthcare is Roth's Noble prize winning work \cite{Roth}.
This work uses matching game algorithms to match medical interns to hospitals.
The purpose of this paper is to discuss some work relevant to congestion and healthcare.

@@

In \cite{Adler1969,Bell1983,Edelson1971,Knudsen1972,Luski1976,Naor1969,Yechiali1972} a variety of models are discussed that obtain optimal and equilibrium behaviour in situations where individuals can choose between a best queue to join.
Most of the work considers these systems in a theoretical context.

@@

The degree of central control that should be exercised is a very important question to be considered by governments and/or policy makers.
What is the effect of allowing individuals to choose service provider?

This is a question that is answered using the Game theoretical concept referred to as the \textit{Price of Anarchy} (PoA).
This was first defined in \cite{Koutsoupias2009} but an excellent introduction is given in \cite{Roughgarden2005}.
The PoA is defined as the ratio of the selfish utility to the optimal utility.

Section \label{sec:choosingqueues} will discuss some PoA analysis applied to individuals choosing between queues.
Section \label{sec:managingqueues} will discuss similar analysis in the case of selfish behaviour related to the management of queues.
Section \label{sec:conclusion} will conclude with a summary and thoughts for further work.

>>>>

The best known work applying Game Theory to Healthcare is Roth's Noble prize winning work \cite{Roth}.
This work uses matching game algorithms to match medical interns to hospitals.
The purpose of this paper is to discuss some work relevant to a different area of healthcare: congestion.

@@

In \cite{Adler1969,Bell1983,Edelson1971,Knudsen1972,Luski1976,Naor1969,Yechiali1972} a variety of models are discussed that obtain optimal and equilibrium behaviour in situations where individuals can choose between a best queue to join.
Most of the work considers these systems in a theoretical context but often comes to a common conclusion:

@@

The degree of central control that should be exercised is a very important question to be considered by governments and/or policy makers.
How do we measure the effect of selfish behaviour?

This is a question that is answered using the Game theoretical concept referred to as the \textit{Price of Anarchy} (PoA).
This was first defined in \cite{Koutsoupias2009} but an excellent overview is given in \cite{Roughgarden2005}.
The PoA is defined as the ratio of the selfish utility to the optimal utility.

Section \ref{sec:choosingqueues} will discuss some PoA analysis applied to individuals choosing between queues.
Section \ref{sec:managingqueues} will discuss similar analysis in the case of selfish behaviour related to the management of queues.
Section \ref{sec:conclusion} will conclude with a summary and thoughts for further work.
